---
title: "get_embed Usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{get_embed Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

The `get_embed` function retrieves embeddings based on provided input data. This vignette demonstrates the usage of the `get_embed` function with example datasets included in the `MUGS` package.

---

## Load the Required Library

Ensure the `MUGS` package is loaded before running the example:

```{r setup}
library(MUGS)
```

---

## Load Example Data

Load the example datasets for the `get_embed` function:

```{r load_data}
set.seed(1)
S <- matrix(rnorm(100^2), 100, 100)
library(rsvd)
svd <- rsvd(S, 20)
```

---

## Run the `get_embed` Function

Run the `get_embed` function to extract embeddings from the data:

```{r run_function}
# Example usage of get_embed
U <- get_embed(svd, d=10, normalize=TRUE)
```

---

## Examine the Output

Explore the structure and key components of the output:

```{r examine_output}
# View the structure of the output
str(U)

# Display the first few rows of the results
cat("\nEmbedding Results (first 5 rows):\n")
print(head(U, 5))
```

---

## Notes

1. **Input Data**: Ensure that `U.1` and `S.1` are properly formatted matrices or data frames.
2. **Output Structure**: The output contains embeddings derived from the input data, which can be used in downstream analysis.

---

## Summary

This vignette demonstrated the use of the `get_embed` function to retrieve embeddings from input data. Use this function to process your data and extract meaningful embeddings for further applications.
