---
title: "GroupEff_par_usage"
output:
  rmarkdown::html_vignette:
    output_dir: "C:/MUGS/MUGS/doc"
vignette: >
  %\VignetteIndexEntry{GroupEff_par_usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

## Introduction

The `GroupEff_par` function estimates group effects using embeddings and structured input data. This vignette demonstrates the usage of the `GroupEff_par` function with example data included in the package.

---

## Load the Required Library

Ensure the `MUGS` package is loaded before running the example:

```{r setup}
library(MUGS)
```

---

## Load the Data

Load the required datasets for the example:

```{r load_data}
# Load required data
data(S.1)
data(S.2)
data(X.group.source)
data(X.group.target)
data(U.1)
data(U.2)
```

---

## Prepare Variables

Prepare the variables required for the `GroupEff_par` function:

```{r prepare_variables}
# Extract names and create name lists
names.list.1 <- rownames(S.1)
names.list.2 <- rownames(S.2)
full.name.list <- c(names.list.1, names.list.2)

# Initialize beta matrix
beta.names.1 <- unique(c(colnames(X.group.source), colnames(X.group.target)))
beta.int <- matrix(0, 400, 10)  # Replace with appropriate dimensions
rownames(beta.int) <- beta.names.1
```

---

## Run the Function

Run the `GroupEff_par` function:

```{r run_function, eval=FALSE}
  GroupEff_par.out <- GroupEff_par(
    S.MGB = S.1, 
    S.BCH = S.2, 
    n.MGB = 2000, 
    n.BCH = 2000, 
    U.MGB = U.1, 
    U.BCH = U.2, 
    V.MGB = U.1, 
    V.BCH = U.2, 
    X.MGB.group = X.group.source, 
    X.BCH.group = X.group.target,
    n.group = 400, 
    name.list = full.name.list, 
    beta.int = beta.int, 
    lambda = 0, 
    p = 10, 
    n.core = 2
  )
```

---

## Examine the Output

Explore the structure and key components of the output:

```{r examine_output}
# View structure of the output
str(GroupEff_par.out)

# Print specific components of the result
cat("\nEstimated Group Effects:\n")
print(GroupEff_par.out$effects[1:5, 1:3])  # Show the first 5 rows and 3 columns of effects

cat("\nRegularization Path:\n")
print(GroupEff_par.out$path)
```

---

## Notes

1. **Custom Parameters**: Modify parameters like `n.MGB`, `n.BCH`, `p`, and `lambda` to test different scenarios.
2. **Data Preparation**: Ensure datasets (`S.1`, `S.2`, `U.1`, `U.2`, etc.) are correctly loaded and aligned.
3. **Output**: Key components include the estimated group effects matrix and regularization path.

---

## Summary

This vignette demonstrated how to use the `GroupEff_par` function for estimating group effects. Adjust input parameters and datasets to test different scenarios and interpret the output components for your analysis.
